WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2013-08-02 ms.tex
Complete Bayesian section

The prevailing technique for detection of \acp{GW} from \acp{CBC} is to realize a \ac{MLE} from the likelihood in \Eref{eq:gaussian-likelihood} and the signal model in \Eref{eq:signal-model}. Concretely, this results in a bank of matched filters, or template waveforms that are convolved with the incoming data stream. The matched filter or \ac{ML} parameter estimates are given by
%
\begin{eqnarray}
\hat{\boldsymbol\theta}_i, \{\hat\tau_i\}_i &=& \argmax_{\boldsymbol\theta_\mathrm{in}, \{\hat\tau_i\}_i} \sum_i \frac{1}{{\sigma_i}^2} \left| \int_0^\infty \frac{h^*(\omega; \boldsymbol\theta_\mathrm{in}) x_i(\omega) e^{-i \omega \tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right|^2 \\
\hat\rho_i &=& \frac{1}{\sigma_i} \left| \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{-i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right| \\
\hat\gamma_i &=& \arg \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{-i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega,
\end{eqnarray}
%
where the $^*$ denotes a complex conjugate.

@@

>>>>

The prevailing technique for detection of \acp{GW} from \acp{CBC} is to realize a \ac{MLE} from the likelihood in \Eref{eq:gaussian-likelihood} and the signal model in \Eref{eq:signal-model}. Concretely, this results in a bank of matched filters, or template waveforms that are convolved with the incoming data stream. The matched filter or \ac{ML} point estimates of the signal parameters are
%
\begin{eqnarray}
\hat{\boldsymbol\theta}_i, \{\hat\tau_i\}_i &=& \argmax_{\boldsymbol\theta_\mathrm{in}, \{\hat\tau_i\}_i} \sum_i \frac{1}{{\sigma_i}^2} \left| \int_0^\infty \frac{h^*(\omega; \boldsymbol\theta_\mathrm{in}) x_i(\omega) e^{-i \omega \tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right|^2 \\
\hat\rho_i &=& \frac{1}{\sigma_i} \left| \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{-i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right| \\
\hat\gamma_i &=& \arg \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{-i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega.
\end{eqnarray}

@@

In what follows, we propose a complementary rapid parameter estimation scheme that can produce reliable positions estimates within minutes of a detection. We can even use our scheme to speed up the full \ac{MCMC} analysis and make the refined parameter estimates available more quickly. The key difference is that we start not from the \ac{GW} signal itself, but from the point parameter estimates from the detection. By harnessing the detection pipeline in this manner, we arrive at a simpler Bayesian problem that is amenable to straightforward, deterministic, numerical quadrature.
